### 2019-07-03 images/flow_basic.tex
first commit

  \node (sample)  [screen, join]  {Screen random documents};
  \node (model) [computer, join, left=of sample]  {Train model,\\ predict relevance};
  \node (screenrel)  [screen, below of =sample]  {Screen most \\ relevant documents};
  \node (stopscreen) [decision, join] {Irrelevant?};

  \node (screenr2) [screen, join]  {Screen random documents};

  \node (recall) [decision, join] {Recall $>$ threshold?};

	\node (sform) [form, right=of screenr2, xshift=-15mm] { Estimate $\hat{p}U$ };

  \node (rform) [form, right=of recall, xshift=-15mm] {$ 1 - \frac{\hat{p}U}{\hat{p}P} \frac{U}{P}$};

  \node (reldocs) [multidoc, below of=recall, xshift=20mm, yshift=-8mm]  {Relevant documents};
  \node (irreldocs) [multidoc, fill=blue!5, below of=recall, xshift=-20mm, yshift=-8mm]  {Irrelevant documents};
  %\node

@@

  \node [coord, left=of stopscreen, xshift=-45mm] (c1)  {}; %\cmark{1} 
  \node [coord, above=of model, yshift=2em] (c2)  {}; %\cmark{1}

  \node [coord, left=of recall, xshift=-45mm] (c3)  {}; %\cmark{1}

 \path (stopscreen.west) to node [very near start, yshift=1em] {$n$} (c1);

 	\draw [o->,norm] (stopscreen.west) -- (c1) |-  (c2) -- (model.north);

  \path (recall.west) to node [very near start, yshift=1em] {$n$} (c3);

 %\draw [o->,norm] (recall.west) -- (c3) |-  (c2) -- (model.north);
 \draw [o->,norm] (recall.west) -- (c3) |-  (screenr2.west);

 \draw [o->,norm] (recall.south) -- (reldocs);
 \draw [o->,norm] (recall.south) -- (irreldocs);

>>>>

  \node (sample)  [screen, join]  {Screen random documents};
  \node (model) [computer, join, left=of sample]  {Train model,\\ predict relevance};
  \node (screenrel)  [screen, below of =sample]  {Screen most \\ relevant documents};
  %\node (stopscreen) [decision, join] {Irrelevant?};

  %\node (screenr2) [screen, join]  {Screen random documents};

  %\node (recall) [decision, join] {Recall $>$ threshold?};

	%\node (sform) [form, right=of screenr2, xshift=-15mm] { Estimate $pU$ };

  %\node (rform) [form, right=of recall, xshift=-15mm] {$ 1 - \frac{pU}{pP} \frac{U}{P}$};

  \node (reldocs) [multidoc, below of=screenrel, xshift=20mm, yshift=-8mm]  {Relevant documents};
  \node (irreldocs) [multidoc, fill=blue!5, below of=screenrel, xshift=-20mm, yshift=-8mm]  {Irrelevant documents};
  %\node

@@

  \node [coord, left=of screenrel, xshift=-45mm, yshift=-10mm] (c1)  {}; %\cmark{1} 
  \node [coord, above=of model, yshift=2em] (c2)  {}; %\cmark{1}

  %\node [coord, left=of recall, xshift=-45mm] (c3)  {}; %\cmark{1}

 %\path (screenrel.south) to node [very near start, yshift=-1em] {$n$} (c1);

 	\draw [o->,norm] (screenrel.south) |- (c1) |-  (c2) -- (model.north);

  %\path (recall.west) to node [very near start, yshift=1em] {$n$} (c3);

 %\draw [o->,norm] (recall.west) -- (c3) |-  (c2) -- (model.north);

 %\draw [o->,norm] (screenrel.south) -- (reldocs);
 %\draw [o->,norm] (screenrel.south) -- (irreldocs);
